\chapter*{参考文献}
\label{ref}
%\addcontentsline{toc}{chapter}{参考文献}
\lhead[参考文献]{}
%\renewcommand{\refname}{引用文献}
\thispagestyle{empty}


\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\textmc{＜和文文献＞}}

\begin{mythebibliography}{99}

\bibitem[厚生労働省 2014]{厚労省2014}
\leavevmode \\
厚生労働省:
\newblock ``平成26年　患者調査の概況'',
\newblock 2014.
\\

\bibitem[厚生労働省 2016]{厚労省2016}
\leavevmode \\
厚生労働省:
\newblock ``平成28年　国民生活基礎調査の概況'',
\newblock 2016.
\\

\bibitem[脳卒中治療ガイドライン 2009]{脳卒中2009}
\leavevmode \\
日本脳卒中学会 脳卒中合同ガイドライン委員会 編:
\newblock ``脳卒中治療ガイドライン2009'',
\newblock http://www.jsts.gr.jp/main08a.html, 2009, 閲覧日2018.12.13.
\\

\bibitem[道免 2015]{道免2015}
\leavevmode \\
道免 和久 編:
\newblock ``ニューロリハビリテーション'',
\newblock 医学書院, 2015.
\\

\bibitem[有末 2015]{有末2015}
\leavevmode \\
有末 伊織, 田中 直次郎, 藤井 靖晃, 藤高 裕太, 中本 舞, 松本 強, 丸田 佳克, 福江 亮, 松下 信郎, 山岡 まこと, 橋本 陽平, 園田 泰, 霜山 香織, 福間 美佑貴, 岡本 隆嗣:
\newblock ``歩行アシストロボットを用いた 回復期脳卒中患者に対する歩行練習の影響 ─歩行速度による違い─'',
\newblock 理学療法科学, Vol.~20, No.~1, pp.~119--123, 2015.
\\

\bibitem[渡邊 2016]{渡邊2016}
\leavevmode \\
渡邊 亜紀, 川井 康平, 佐藤 浩二, 宮崎 吉孝, 伊藤 寿弘, 森 照明:
\newblock ``HONDA歩行アシストの継続使用による脳卒中片麻痺者の歩行変化'',
\newblock 理学療法学, Vol.~43, No.~4, pp.~337--341, 2016.
\\

\bibitem[長田 2012]{長田2012}
\leavevmode \\
長田 悠路, 山本 澄子, 渕 雅子:
\newblock ``脳卒中片麻痺患者の起立動作における運動学的・運動力学的評価指標'',
\newblock 理学療法学, Vol.~39, No.~3, pp.~149--158, 2012.
\\

\bibitem[津坂 2017]{津坂2017}
\leavevmode \\
津坂 優子, F. Dallalibera, 岡崎 安直, 山本 正樹, 横小路 泰義:
\newblock ``理学療法士のスキルを活かした自立支援型起立アシストロボットの開発'',
\newblock 日本機械学会論文集, Vol.~83, No.~852, pp.~1--14, 2017.
\\

%\bibitem[橋本 2001]{橋本2001}
%\leavevmode \\
%橋本 秀紀, 秋山 尊志:
%\newblock ``空間知能化―インテリジェント・スペースの提案'',
%\newblock 生産研究, Vol.~53, No.~5, pp.~257--267, 2001.
%\\

%\end{mythebibliography}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\textmc{\hspace{-1zw}＜英文文献＞}}

\bibitem[Guralnik 1994]{Guralnik1994}
\leavevmode \\
J. M. Guralnik, E. M. Simonsick, L. Ferrucci, R. J. Glynn, L. F. Berkman, D. G. Blazer, P. A. Scherr and R. B. Wallace:
\newblock ``A Short Physical Performance Battery Assessing Lower Extremity Function: Association with Self-Reported Disability and Prediction of Mortality and Nursing Home Admission'',
\newblock {\itshape Journals of Gerontology}, Vol.~49, No.~2, pp.~85--94, 1994. 
\\

\bibitem[Fisher 2011]{Fisher2011}
\leavevmode \\
S. Fisher, L. Lucas and T. A. Thrasher:
\newblock ``Robot-Assisted Gait Training for Patients with Hemiparesis Due to Stroke'',
\newblock {\itshape Topics in Stroke Rehabilitation}, Vol.~18, No.~3, 2011. 
\\

\bibitem[Srivastava 2016]{Srivastava2016}
\leavevmode \\
S. Srivastava, P. C. Kao, D. S. Reisman, J. P. Scholz and S. K. Agrawal:
\newblock ``Robotic assist-as-needed as an alternative to therapist-assisted gait rehabilitation'',
\newblock {\itshape International journal of physical medicine \& rehabilitation}, Vol.~4, No.~5, pp.~370, 2016. 
\\

\bibitem[Chou 2003]{Chou2003}
\leavevmode \\
S. W. Chou, A. M. K. Wong, C. P. Leong, W. S. Hong, F. K. Tang and T. H. Lin:
\newblock ``Postural control during sit-to stand and gait in stroke patients'',
\newblock {\itshape American Journal of Physical Medicine and Rehabilitation}, vol.~82, no.~1, pp.~42--47, 2003.
\\

\bibitem[Tsukahara 2010]{Tsukahara2010}
\leavevmode \\
A. Tsukahara, R. Kawanishi, Y. Hasegawa and Y. Sankai:
\newblock ``Sit-to-stand and stand-to-sit transfer support for complete paraplegic patients with robot suit HAL'',
\newblock {\itshape Advanced Robotics}, Vol.~24, No.~11, pp.~1615--1638, 2010. 
\\

\bibitem[Shiraishi 2016]{Shiraishi2016}
\leavevmode \\
R. Shiraishi, H. Kawamoto and Y. Sankai:
\newblock ``Development of sit-to-stand and stand-to-sit training system for hemiplegie patients'',
\newblock {\itshape Proceedings of the Annual International Conference of the IEEE Engineering in Medicine and Biology Society}, pp.~4567--4572, 2016. 
\\

\bibitem[Mourey 2000]{Mourey2000}
F. Mourey, A. Grishin, P. D'Athis, T. Pozzo and P. Stapley:
\newblock ``Standing up from a chair as a dynamic equilibrium task: a comparison between young and elderly subjects'',
\newblock {\itshape The journals of gerontology. Series A, Biological sciences and medical sciences}, vol.~55, no.~9, pp.~B425--B431, 2000.
\\

\bibitem[Yang 2017]{Yang2017}
N. Yang, Q. An, H. Yamakawa, Y. Tamura, A. Yamashita, K. Takahashi, M. Kinomoto, H. Yamasaki, M. Itkonen, F. S. Alnajjar, S. Shimoda, H. Asama, N. Hattori and I. Miyai:
\newblock ``Clarification of muscle synergy structure during standing-up motion of healthy young, elderly and post-stroke patients'',
\newblock {\itshape 2017 International Conference on Rehabilitation Robotics (ICORR)}, pp.~19--24, 2017.
\\

\bibitem[Silva 2013]{Silva2013}
A. Silva, A. S. P. Sousa, R. Pinheiro, J. Ferraz, J. M. R. S. Tavares, R. Santos and F. Sousa:
\newblock ``Activation timing of soleus and tibialis anterior muscles during sit-to-stand and stand-to-sit in post-stroke vs. healthy subjects'',
\newblock {\itshape Somatosensory and Motor Research}, vol.~30, No.~1,  pp.~48--55, 2013.
\\

%\bibitem[Huges 1994]{Hughes1994}
%\leavevmode \\
%M. A. Hughes, D. K. Weiner, M. L. Schenkman, R. M. Long and S. A. Studenski:
%\newblock ``Chair rise strategies in the elderly'',
%\newblock {\itshape Clinical Biomechanics}, vol.~9, no.~3, pp.~187--192, 1994.

\bibitem[Gross 1998]{Gross1998}
\leavevmode \\
M. M. Gross, P. J. Stevenson, S. L. Charette, G. Pyka and R. Marcus:
\newblock ``Effect of muscle strength and movement speed on the biomechanics of rising from a chair in healthy elderly and young women'',
\newblock {\itshape  Gait and Posture}, vol.~8, no.~3, pp.~175--185, 1998.
\\

%\bibitem[Brunt 2002]{Brunt2002}
%D. Brunt, B. Greenberg, S. Wankadia, M. A. Trimble and O. Shechtman:
%\newblock ``The effect of foot placement on sit to stand in healthy young subjects and patients with hemiplegia'',
%\newblock {\itshape Archives of Physical Medicine and Rehabilitation}, vol.~83, no.~7, pp.~924--929, 2002.
%\\

\bibitem[Chugo 2007]{Chugo2007}
D. Chugo, K. Kawabata, H. Okamoto, H. Kaetsu, H. Asama, N. Miyake, K. Kosuge:
\newblock ``Force assistance system for standing up motion'',
\newblock {\itshape Industrial Robot: An International Journal}, Vol.~34, No.~2, pp.~128--134, 2007.
\\

\bibitem[Tsusaka 2015]{Tsusaka2015}
Y. Tsusaka, Y. Okazaki, Y. Fudaba, R. Futakuchi, M. Yamamoto, N. Shikata, M. Terashima, T. Funatani, H. Shima:
\newblock ``Development of standing-up motion assist robot to realize physiotherapist skill for muscle strength maintenance'',
\newblock {\itshape Proceedings - IEEE International Workshop on Robot and Human Interactive Communication}, pp.~140--145, 2015.
\\

\clearpage

\end{mythebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
