\chapter*{参考文献}
%\addcontentsline{toc}{chapter}{参考文献}
\lhead[参考文献]{}
%\renewcommand{\refname}{引用文献}
\thispagestyle{empty}

\newpage

%==============================================================================
%和文文献
%==============================================================================
\subsection*{\textmc{＜和文文献＞}}
\begin{mythebibliography}{}

%\bibitem[井上 2015]{井上2015}
%\leavevmode \\井上 優希, 董 阿飛, 田平 創, 鳥居 秋彦, 奥富 正敏:
%\newblock ``全球パノラマ画像を用いたSfMによる3次元復元と自己位置・方位推定への応用'',
%\newblock 精密工学会誌, Vol.~81, No.~12, pp.~1173--1179, 2015.
%\\

%\bibitem[大津 2014]{大津2014}
%\leavevmode \\大津 恭平, 久保田 孝:
%\newblock ``特徴の少ない地形における惑星探査ローバのビジュアルオドメトリ法'',
%\newblock 日本ロボット学会誌, Vol.~32, No.~9, pp.~825--831, 2014.
%\\

\bibitem[酒井 2014]{酒井2014}
\leavevmode \\酒井 研斗, 堀 浩一:
\newblock ``小型UAVによる自律分散型SLAMシステムの実証研究'',
\newblock 人工知能学会全国大会論文集, Vol.~28, pp.~1--4, 2014.
\\

%\bibitem[角谷 2016]{角谷2016}
%\leavevmode \\角谷 和宣, 繁田 亮, 川原 圭博, 浅見 徹, 蒲谷 直樹:
%\newblock ``低価格移動式農業用ロボットのためのウェブカメラを用いた自己位置推定'',
%\newblock 電子情報通信学会技術研究報告, Vol.~116, No.~308, pp.~79--84, 2016.
%\\

\bibitem[ゾリーグ 2014]{ゾリーグ2014}
\leavevmode \\ゾリーグ アナラ, 萩庭 篤史, 佐藤 裕幸:
\newblock ``タブレットPCを用いたAGVの自立走行制御における走行精度の向上'',
\newblock 電子情報通信学会技術研究報告, Vol.~113, No.~433, pp.~93--98, 2014.
\\

%\bibitem[橋本 2001]{橋本2001}
%\leavevmode \\橋本 秀紀, 秋山 尊志:
%\newblock ``空間知能化―インテリジェント・スペースの提案'',
%\newblock 生産研究, Vol.~53, No.~5, pp.~257--267, 2001.
%\\

\bibitem[八木 2001]{八木2001}
\leavevmode \\八木 康史, 横矢 直和:
\newblock ``全方位ビジョン：センサ開発と応用の最新動向'',
\newblock 精密工学会誌, Vol.~81, No.~12, pp.~1173--1179, 2015.
\\

\bibitem[ELECOM]{ELECOM}
\leavevmode \\エレコム株式会社:
\newblock 半天球360度カメラ,\\
\newblock http://www2.elecom.co.jp/products/ACAM-VRS01BK.html (閲覧日 2019.12.16).
\\

\bibitem[Panasonic]{Panasonic}
\leavevmode \\パナソニック株式会社:
\newblock 全方位ネットワークカメラ,\\
\newblock https://sol.panasonic.biz/security/camera/ipro\_hd/sfv481\_sfn480/ (閲覧日 2019.12.16).
\\

\bibitem[RICOH]{RICOH}
\leavevmode \\株式会社リコー:
\newblock RICOH THETA,\\
\newblock https://theta360.com/ja/ (閲覧日 2019.12.16).
\\

\bibitem[VSTONE]{VSTONE}
\leavevmode \\ヴイストン株式会社:
\newblock 全方位センサ・全方位カメラ,\\
\newblock http://www.vstone.co.jp/products/sensor\_camera/ (閲覧日 2019.12.16).
\\


%\bibitem[東京電力株式会社 HP]{東京電力株式会社HP}
%\leavevmode \\東京電力株式会社:
%\newblock 福島第一原発原子炉建屋周辺の様子（画像）,\\
%\newblock http://photo.tepco.co.jp/cat2/01-j.html, 2014.
%\\


\newpage
%==============================================================================
%英文文献
%==============================================================================
\subsection*{\textmc{\hspace{-1zw}＜英文文献＞}}

\bibitem[Aihara 1998]{Aihara1998} 
\leavevmode \\N.~Aihara, H.~Iwasa, N.~Yokoya and H.~Takemura:
\newblock ``Memory-based Self-localization Using Omnidirectional Images'',
\newblock Proceedings of the 14th International Conference on Pattern Recognition, pp.~1799--1803, 1998.
\\

%\bibitem[Alcantarilla 2013]{Alcantarilla2013} 
%\leavevmode \\P.~F.~Alcantarilla, J.~Nuevo and A.~Bartoli:
%\newblock ``Fast Explicit Diffusion for Accelerated Features in Nonlinear Scale Spaces'',
%\newblock Proceedings of the British Machine Vision Conference, pp.~1--11, 2013.
%\\

%\bibitem[Aldoma 2011]{Aldoma2011} 
%\leavevmode \\A.~Aldoma and M.~Vincze:
%\newblock ``CAD-Model Recognition and 6DOF Pose Estimation Using 3D Cues'',
%\newblock Proceedings of the 2011 IEEE International Conference on Computer Vision, pp.~585--592, 2011.
%\\

\bibitem[Antone 2000]{Antone2000} 
\leavevmode \\M.~E.~Antone and S.~Teller:
\newblock ``Automatic Recovery of Relative Camera Rotation for Urban Scenes'',
\newblock Proceedings of the 2000 IEEE Conference on Computer Vision and Pattern Recognition, pp.~282--289, 2000.
\\

\bibitem[Arulampalam 2002]{Arulampalam2002} 
\leavevmode \\M.~S.~Arulampalam, S.~Maskel, N.~Gordon and T.~Clapp:
\newblock ``A Tutorial on Particle Filters for Online Nonlinear/Non-Gaussian Bayesian Tracking'',
\newblock IEEE Transactions on Signal Processing, Vol.~50, No.~2, pp.~174--188, 2002.
\\

\bibitem[Arulampalam 2004]{Arulampalam2004} 
\leavevmode \\S.~Arulampalam, N.~Gordon and B.~Ristic:
\newblock Beyond the Kalman Filter: Particle Filters for Tracking Applications,
\newblock Aetech House, 2004.
\\

%\bibitem[Barcel\'{o} 2000]{Barcel\'{o}2000}
%\leavevmode \\J.~A.~Barcel\'{o}, M.~Forte and D.~H.~Sanders:
%\newblock Virtual Reality in Archaeology,
%\newblock ArchaeoPress Oxford, UK, 2000.
%\\

\bibitem[Bazin 2012a]{Bazin2012a} 
\leavevmode \\J.~C.~Bazin, C.~Demonceaux, P.~Vasseur and I.~Kweon:
\newblock ``Rotation Estimation and Vanishing Point Extraction by Omnidirectional Vision in Urban Environment'',
\newblock The International Journal of Robotics Research, Vol.~31, No.~1, pp.~63--81, 2012.
\\

\bibitem[Bazin 2012b]{Bazin2012b} 
\leavevmode \\J.~C.~Bazion and M.~Pollefeys:
\newblock ``3-line RANSAC for Orthogonal Vanishing Point Detection'',
\newblock Proceedings of the 2012 IEEE/RSJ International Conference on Intelligent Robots and Systems, pp.~4282--4287, 2012.
\\

\newpage

\bibitem[Blender]{Blender} 
\leavevmode \\blender.org:
\newblock Blender,\\
\newblock https://www.blender.org/ (閲覧日 2019.12.16).
\\

\bibitem[Bleser 2006]{Bleser2006} 
\leavevmode \\G.~Bleser, H.~Wuest and D.~Stricker:
\newblock ``Online Camera Pose Estimation in Partially Known and Dynamic Scenes'',
\newblock Proceedings of the 5th IEEE/ACM International Symposium on Mixed and Augmented Reality, pp.~56--65, 2006.
\\

\bibitem[Canny 1986]{Canny1986} 
\leavevmode \\J.~Canny:
\newblock ``A Computational Approach to Edge Detection'',
\newblock IEEE Transaction on Pattern Analysis and Machine Intelligence, Vol.~8, No.~6, pp.~679--698, 1986.
\\

\bibitem[Caron 2012]{Caron2012} 
\leavevmode \\G.~Caron, E.~M.~Mouaddib and E.~Marchand:
\newblock ``3D Model Based Tracking for Omnidirectional Vision: A New Spherical Approach'',
\newblock Robotics and Autonomous Systems, Vol.~60, No.~8, pp.~1056--1068, 2012.
\\

\bibitem[Caruso 2015]{Caruso2015} 
\leavevmode \\D.~Caruso, J.~Engel and D.~Cremers:
\newblock ``Large-Scale Direct SLAM for Omnidirectional Cameras'',
\newblock Proceedings of the 2015 IEEE/RSJ International Conference on Intelligent Robots and System, pp.~141--148, 2015.
\\

\bibitem[Cham 2010]{Cham2010} 
\leavevmode \\T.~Cham, A.~Ciptadi, W.~Tan, M.~Pham and L.~Chia:
\newblock ``Estimating Camera Pose from a Single Urban Ground-View Omnidirectional Image and a 2D Building Outline Map'',
\newblock Proceedings of the 2010 IEEE International Conference on Computer Vision and Pattern Recognition, pp.~366--373, 2010.
\\

%\bibitem[Cheng 2006]{Cheng2006} 
%\leavevmode \\Y.~Cheng, M.~W.~Maimone and L.~Matthies:
%\newblock ``Visual Odometry on the Mars Exploration Rovers - A Tool to Ensure Accurate Driving and Science imaging'',
%\newblock IEEE Robotics \& Automation Magazine, Vol.~13, No.~2, pp.~54--62, 2006.
%\\

\newpage

\bibitem[Coughlan 2001]{Coughlan2001} 
\leavevmode \\J.~M.~Coughlan and A.~L.~Yuille:
\newblock ``The Manhattan World Assumption: Regularities in Scene Statistics Which Enable Bayesian Inference'',
\newblock Proceedings of the Advances in Neural Information Processing Systems, pp.~845--851, 2001.
\\

%\bibitem[Demonceaux 2006]{Demonceaux2006}
%\leavevmode \\C.~Demonceaux, P.~Vasseur and C.~Pegard:
%\newblock ``UAV Attitude Computation by Omnidirectional Vision in Urban Environment'',
%\newblock Proceedings of the 2007 IEEE International Conference on Robotics and Automation, pp.~2017--2022, 2006.
%\\

\bibitem[Denis 2008]{Denis2008}
\leavevmode \\P.~Denis, J.~H.~Elder and F.~J.~Estrada:
\newblock ``Efficient Edge-based Methods for Estimating Manhattan Frames in Urban Imagery'',
\newblock Proceedings of the 2008 European Conference on Computer Vision, pp.~197--210, 2008.
\\

\bibitem[Elloumi 2012]{Elloumi2012}
\leavevmode \\W.~Elloumi, S.~Treuillet and R.~Leconge:
\newblock ``Tracking Orthogonal Vanishing Points in Video Sequences for Reliable Camera Orientation in Manhattan World'',
\newblock Proceedings of the 5th International Congress on Image and Signal Processing, pp.~128--132, 2012.
\\

\bibitem[Elloumi 2013]{Elloumi2013}
\leavevmode \\W.~Elloumi, S.~Treuillet and R.~Leconge:
\newblock ``Real-time Estimation of Camera Orientation by Tracking Orthogonal Vanishing Points in Videos'',
\newblock Proceedings of the 2013 International Conference on Computer Vision Theory and Applications, pp.~215--222, 2013.
\\

%\bibitem[Engel 2013]{Engel2013}
%\leavevmode \\J.~Engel, J.~Sturm and D.~Cremers:
%\newblock ``Semi-dense Visual Odometry for a Monocular Camera'',
%\newblock Proceedings of the 2013 International Conference on Computer Vision, pp.~1449--1456, 2013.
%\\

%\bibitem[Engel 2014]{Engel2014}
%\leavevmode \\J.~Engel, T.~Sch\.{o}ps and D.~Cremers:
%\newblock ``Large-Scale Direct Monocular SLAM'',
%\newblock Proceedings of the 2014 European Conference on Computer Vision, pp.~834--849, 2014.
%\\

%\bibitem[Engel 2015]{Engel2015} 
%\leavevmode \\J.~Engel, J.~St\.{u}cker and D.~Cremers:
%\newblock ``Large-Scale Direct SLAM with Stereo Cameras'',
%\newblock Proceedings of the 2015 IEEE/RSJ International Conference on Intelligent Robots and Systems, pp.~1935--1942, 2015.
%\\

%\bibitem[Engel 2017]{Engel2017} 
%\leavevmode \\J.~Engel, V.~Koltun and D.~Cremers:
%\newblock ``Direct Sparse Odometry'',
%\newblock IEEE Transactions on Pattern Analysis and Machine Intelligence, DOI 10.1109/TPAMI.2017.2658577, 2017.
%\\

\bibitem[Fischler 1981]{Fischler1981} 
\leavevmode \\M.~A.~Fischler and R.~C.~Bolles:
\newblock ``Random Sample Consensus: A Paradigm for Model Fitting with Applications to Image Analysis and Automated Cartography'',
\newblock Communications of the ACM, Vol.~24, No.~6, pp.~381--395, 1981.
\\

%\bibitem[Forster 2014]{Forster2014} 
%\leavevmode \\C.~Forster, M.~Pizzoli and D.~Scaramuzza:
%\newblock ``SVO: Fast Semi-Direct Monocular Visual Odometry'',
%\newblock Proceedings of the 2014 IEEE International Conference on Robotics and Automation, pp.~15--22, 2014.
%\\


\bibitem[Forster 2017]{Forster2017} 
\leavevmode \\C.~Forster, Z.~Zhang, M.~Gassner, M.~Werlberger and D.~Scaramuzza:
\newblock ``SVO: Semi-Direct Visual Odometry for Monocular and Multi-camera Systems'',
\newblock IEEE Transactions on Robotics, Vol.~33, No.~2, pp.~249--265, 2017.
\\

%\bibitem[George 2015]{George2015} 
%\leavevmode \\M.~George, JP.~Tardif and A.~Kelly:
%\newblock ``Visual and Inertial Odometry for a Disaster Recovery Humanoid'',
%\newblock Proceedings of the 9th Conference on Field and Service Robotics, Vol.~105, pp.~501--514, 2015.
%\\

\newpage

\bibitem[Goto 2018]{Goto2018} 
\leavevmode \\T.~Goto, S.~Pathak, Y.~Ji, H.~Fujii, A.~Yamashita and H.~Asama:
\newblock ``Line-based Global Localization of a Spherical Camera in Manhattan Worlds'',
\newblock Proceedings of the 2018 IEEE International Conference on Robotics and Automation, pp.~2269--2303, 2018.
\\

\bibitem[Grauman 2004]{Grauman2004} 
\leavevmode \\K.~Grauman and T.~Darrell:
\newblock ``Fast Contour Matching Using Approximate Earth Mover's Distance'',
\newblock Proceedings of the 2004 IEEE International Conference on Computer Vision and Pattern Recognition, pp.~220--227, 2004.
\\

\bibitem[Hada 2017]{Hada2017} 
\leavevmode \\Y.~Hada, M.~Nakao, M.~Yamada, H.~Kobayashi, N.~Sawasaki, K.~Yokoji, S.~Kanai, F.~Tanaka, H.~Date, S.~Pathak, A.~Yamashita, M.~Yamada and T.~Sugihara:
\newblock ``Development of a Bridge Inspection Support System Using Two-wheeled Multicopter and 3D Modeling Technology'',
\newblock Journal of Disaster Research, Vol.~12, No.~3, pp.~593--606, 2017.
\\

\bibitem[Hartley 1997]{Hartley1997}
\leavevmode \\R.~I.~Hartley:
\newblock ``In Defense of the Eight-point Algorithm'',
\newblock IEEE Transactions on Pattern Analysis and Machine Intelligence, Vol.~19, No.~6, pp.~580--593, 1997.
\\


\bibitem[Hartley 2004]{Hartley2004}
\leavevmode \\R.~I.~Hartley and A.~Zisserman:
\newblock Multiple View Geometry in Computer Vision,
\newblock Cambridge University Press, Second Edition, 2004.
\\

%\bibitem[Huang 1994]{Huang1994}
%\leavevmode \\T.~S.~Huang and A.~N.~Netravali:
%\newblock``Motion and Structure from Feature Correspondences: A Review'',
%\newblock Proceedings of the IEEE, Vol.~82, No.~2, pp.~252--268, 1994.
%\\

\bibitem[Ishizuka 2011]{Ishizuka2011}
\leavevmode \\D.~Ishizuka, R.~Kawanishi, T.~Kaneko, A.~Yamashita and H.~Asama:
\newblock``Self-localization of Mobile Robot Equipped with Omnidirectional Camera Using Image Matching and 3D-2D Edge Matching'',
\newblock Proceedings of the 2011 IEEE International Conference on Computer Vision Workshop, pp.~272--279, 2011.
\\

\newpage

\bibitem[Ji 2017]{Ji2017}
\leavevmode \\Y.~Ji, A.~Yamashita and H.~Asama:
\newblock``Automatic Calibration of Camera Sensor Networks Based on 3D Texture Map Information'',
\newblock Robotics and Autonomous Systems, Vol.~87, pp.~313--328, 2017.
\\

\bibitem[Kim 2007]{Kim2007} 
\leavevmode \\S.~Kim, C.~Roh, S.~Kang and M.~Park:
\newblock ``Outdoor Navigation of a Mobile Robot Using Different GPS and Curb Detection'',
\newblock Proceedings of the 2007 IEEE International Conference on Robotics and Automation, pp.~3414--3419, 2007.
\\

\bibitem[Kim 2017]{Kim2017} 
\leavevmode \\P.~Kim, B.~Coltin and H.~J.~Kim:
\newblock ``Visual Odometry with Drift-free Rotation Estimation Using Indoor Scene Regularities'',
\newblock Proceedings of the 2017 British Machine Vision Conference, pp.~1--12, 2017.
\\

\bibitem[Kim 2019]{Kim2019} 
\leavevmode \\D.~Kim, S.~Pathak, A.~Moro, R.~Komatsu, A.~Yamashita and H.~Asama:
\newblock ``E-CNN: Accurate Spherical Camera Rotation Estimation via Uniformization of Distorted Optical Flow Fields'',
\newblock Proceedings of the 2019 IEEE International Conference on Acoustic, Speech and Signal Processing, pp.~2232--2236, 2019.
\\

\bibitem[Klein 2007]{Klein2007}
\leavevmode \\G.~Klein and D.~Murray:
\newblock ``Parallel Tracking and Mapping for Small AR Workspaces'',
\newblock Proceedings of the 6th IEEE/ACM International Symposium on Mixed and Augmented Reality, pp.~225--234, 2007.
\\

\bibitem[Kuipers 1999]{Kuipers1999}
\leavevmode \\J.~B.~Kuipers:
\newblock ``Quaternions and Rotation Sequences'',
\newblock Princeton: Princeton University Press, Vol.~66, pp.~127--143, 1999.
\\

%\bibitem[Lee 2002]{Lee2002} 
%\leavevmode \\J.~H.~Lee and H.~Hashimoto:
%\newblock ``Intelligent Space-Concept and Contents'',
%\newblock Advanced Robotics, Vol.~16, No.~3, pp.~265--280, 2002.
%\\

\newpage

\bibitem[Lee 2015]{Lee2015} 
\leavevmode \\J.~K.~Lee and K.~J.~Yoon:
\newblock ``Real-time Joint Estimation of Camera Orientation and Vanishing Points'',
\newblock Proceedings of the 2015 IEEE Conference on Computer Vision and Pattern Recognition, pp.~1866--1874, 2015.
\\

\bibitem[LG 360]{LG360} 
\leavevmode \\LG Electronics Incorporated:
\newblock LG 360 CAM,\\
\newblock http://www.lg.com/us/mobile-accessories/lg-LGR105AVRZTS-360-cam/ (閲覧日 2019.12.16).
\\

\bibitem[Li 2012]{Li2012} 
\leavevmode \\S.~Li and H.~Jia:
\newblock ``Vanishing Point Estimation by Spherical Gradient'',
\newblock Proceedings of the 21th International Conference on Pattern Recognition, pp.~902--905, 2012.
\\

\bibitem[Lourakis 2004]{Lourakis2004}
\leavevmode \\M.~Lourakis:
\newblock ``Levmar: Levenberg-Marquardt Nonlinear Least Squares Algorithms in C/C++'',
\newblock http://www.ics.forth.gr/~lourakis/levmar/, 2004 (閲覧日 2019.12.16).
\\

\bibitem[Makadia 2003]{Makadia2003} 
\leavevmode \\A.~Makadia and K.~Daniilidis:
\newblock ``Direct 3D-Rotation Estimation from Spherical Images via a Generalized Shift Theorem'',
\newblock Proceedings of the 2013 IEEE Computer Society Conference on Computer Vision and Pattern Recognition, Vol.~2, pp.~210--217, 2003.
\\

\bibitem[Makadia 2004]{Makadia2004} 
\leavevmode \\A.~Makadia, L.~Sorgi and K.~Daniilidis:
\newblock ``Rotation Estimation from Spherical Images'',
\newblock Proceedings of the 17th International Conference on Pattern Recognition, pp.~590--593, 2004.
\\

\bibitem[Makadia 2006]{Makadia2006} 
\leavevmode \\A.~Makadia and K.~Daniilidis:
\newblock ``Rotation Recovery from Spherical Images without Correspondences'',
\newblock IEEE Transactions on Pattern Analysis and Machine Intelligence, Vol.~28, No.~7, pp.~1170--1175, 2006.
\\

\bibitem[Mariottini 2007]{Mariottini2007} 
\leavevmode \\G.~L.~Mariottini and D.~Prattichizzo:
\newblock ``Uncalibrated Video Compass for Mobile Robots from Paracatadioptric Line Images'',
\newblock Proceedings of the 2007 IEEE/RSJ International Conference on Intelligent Robots and Systems, pp.~226--231, 2007.
\\

\bibitem[Marquardt 1963]{Marquardt1963} 
\leavevmode \\D.~W.~Marquardt:
\newblock ``An Algorithm for Least-squares Estimation on Non-linear Parameters'',
\newblock Journal of the Society for Industrial and Applied Mathematics, Vol.~11, No.~2, pp.~431--441, 1963.
\\

\bibitem[Martins 2005]{Martins2005} 
\leavevmode \\A.~Martins, P.~Aguiar and M.~Figueiredo:
\newblock ``Orientation in Manhattan: Equiprojective Classes and Sequential Estimation'',
\newblock IEEE Transactions on Pattern Analysis and Machine Intelligence, Vol.~27, No.~5, pp.~822--826, 2005.
\\

\bibitem[Minagawa 2000]{Minagawa2000} 
\leavevmode \\A.~Minagawa, N.~Tagawa, T.~Moriya and T.~Gotoh:
\newblock ``Vanishing Point and Vanishing Line Estimation with Line Clustering'',
\newblock IEICE Transactions on Information and Systems, Vol.~83, No.~7, pp.~1574--1582, 2000.
\\

\bibitem[Miyagusuku 2016]{Miyagusuku2016} 
\leavevmode \\R.~Miyagusuku, A.~Yamashita and H.~Asama:
\newblock ``Improving Gaussian Processes Based Mapping of Wireless Signals Using Path Loss Models'',
\newblock Proceedings of the 2016 IEEE/RSJ International Conference on Intelligent Robots and Systems, pp.~4610--4615, 2016.
\\

\bibitem[Mirzaei 2011]{Mirzaei2011} 
\leavevmode \\F.~M.~Mirzaei and S.~I.~Roumeliotis:
\newblock ``Globally Optimal Pose Estimation from Line Correspondences'',
\newblock Proceedings of the 2011 IEEE International Conference on Robotics and Automation, pp.~5581--5588, 2011.
\\

\newpage

\bibitem[Nist\'{e}r 2004]{Nister2004} 
\leavevmode \\D.
~Nist\'{e}r, O.~Naroditsky and J.~Bergen:
\newblock ``Visual Odometry'',
\newblock Proceedings of the 2004 IEEE International Conference on Computer Vision and Pattern Recognition, pp.~652--659, 2004.
\\

%\bibitem[Newcombe 2011]{Newcombe2011} 
%\leavevmode \\R.~A.~Newcombe, S.~J.~Lovegrove and A.~J.~Davison:
%\newblock ``DTAM: Dense Tracking and Mapping in Real-time'',
%\newblock Proceedings of the 2011 IEEE International Conference on Computer Vision, pp.~2320--2327, 2011.
%\\

%\bibitem[Nozaki 2016]{Nozaki2016} 
%\leavevmode \\S.~Nozaki, M.~Kimura, G.~Masuyama and K.~Umeda:
%\newblock ``High-speed Three-dimensional Mapping by Direct Estimation of a Small Motion Using Range Images'',
%\newblock Proceedings of the 11th France-Japan Congress on Mechatronics / the 9th Europe-Asia Congress on Mechatronics / the 17th International Conference on Research and Education in Mechatronics, pp.~68--73, 2016.
%\\

\bibitem[Ohno 2004]{Ohno2004} 
\leavevmode \\K.~Ohno, T.~Tsubouchi, B.~Shigematsu and S.~Yuta:
\newblock ``Differencial GPS and Odometry-based Outdoor Navigation of a Mobile Robot'',
\newblock Advanced Robotics, Vol.~18, No.~6, pp.~611--635, 2004.
\\

\bibitem[Olson 2011]{Olson2011} 
\leavevmode \\E.~Olson:
\newblock ``Apriltag: A Robust and Flexible Visual Fiducial System'',
\newblock Proceedings of the 2011 IEEE International Conference on Robotics and Automation, pp.~3400--3407, 2011.
\\

%\bibitem[Orson 2003]{Orson2003} 
%\leavevmode \\C.~F.~Orson, L.~Matthies, M.~W.~Schoppers and M.~Maimone:
%\newblock ``Rover Navigation Using Stereo Ego-motion'',
%\newblock Robotics and Autonomous Systems, Vol.~43, No.~4, pp.~215--229, 2003.
%\\

\bibitem[Pagani 2011]{Pagani2011} 
\leavevmode \\A.~Pagani and D.~Stricker:
\newblock ``Structure from Motion Using Full Spherical Panoramic Cameras'',
\newblock Proceedings of the 2011 IEEE International Conference on Computer Vision Workshops, pp.~375--382, 2011.
\\

%\bibitem[Pathak 2016]{Pathak2016} 
%\leavevmode \\S.~Pathak, A.~Moro, A.~Yamashita and H.~Asama:
%\newblock ``Dense 3D Reconstruction from Two Spherical Images via Optical Flow-based Equirectangular Epipolar Rectification'',
%\newblock Proceedings of the 2016 IEEE International Conference on Imaging Systems and Techniques, pp.~140--145, 2016.
%\\

%\bibitem[Pathak 2017a]{Pathak2017a} 
%\leavevmode \\S.~Pathak, A.~Moro, A.~Yamashita and H.~Asama:
%\newblock ``Optical Flow-based Epipolar Estimation of Spherical Image Pairs for 3D Reconstruction'',
%\newblock Proceedings of the 2017 SICE Journal of Control, Measurement, and System Integration, Vol.~10, No.~5, pp.~476--485, 2017.
%\\

\bibitem[Pathak 2017]{Pathak2017} 
\leavevmode \\S.~Pathak:
\newblock Motion Estimation of Spherical Cameras and 3D Reconstruction Based on Sparse and Dense Pixel Flows,
\newblock Ph.D.~Thesis, The University of Tokyo, 2017.
\\

%\bibitem[Pertile 2016a]{Pertile2016a} 
%\leavevmode \\M.~Pertile, S.~Chiodini, S.~Debei and E.~Lorenzini:
%\newblock ``Uncertainty Comparison of Three Visual Odometry Systems in Different Operative Conditions'',
%\newblock Measurement, Vol.~78, pp.~388--396, 2016.
%\\

%\bibitem[Pertile 2016b]{Pertile2016b} 
%\leavevmode \\M.~Pertile, S.~Chiodini, R.~Giubilato and S.~Debei:
%\newblock ``Effect of Rolling Shutter on Visual Odometry Systems Suitable for Planetary Exploration'',
%\newblock Proceedings of the 2016 IEEE Metrology for Aerospace, pp.~598--603, 2016.
%\\

\bibitem[Rabin 2008]{Rabin2008} 
\leavevmode \\J.~Rabin, J.~Delon and Y.~Gousseau:
\newblock ``Circular Earth Mover's Distance for the Comparison of Local Features'',
\newblock Proceedings of the 19th International Conference on Pattern Recognition, pp.~3576--3579, 2008.
\\

\bibitem[Ramalingam 2011]{Ramalingam2011} 
\leavevmode \\S.~Ramalingam, S.~Bouaziz, P.~Sturm and M.~Brand:
\newblock ``Geolocalization Using Skylines from Omni-Image'',
\newblock Proceedings of the 2011 IEEE International Conference on Computer Vision Workshop, pp.~23--30, 2011.
\\

\bibitem[Rubner 1998]{Rubner1998} 
\leavevmode \\Y.~Rubner, C.~Tomasi and L.~J.~Guibas:
\newblock ``A Metric for Distributions with Application to Image Databases'',
\newblock Proceedings of the 1998 IEEE International Conference on Computer Vision, pp.~59--66, 1998.
\\

%\bibitem[Salvi 2007]{Salvi2007} 
%\leavevmode \\J.~Salvi, C.~Matabosch, D.~Fofi and J.~Forest:
%\newblock ``A Review of Recent Range Image Registration Methods with Accuracy Evaluation'',
%\newblock Image and Vision Computing, Vol.~25, No.~5, pp.~578--596, 2007.
%\\

\bibitem[Samsung]{Samsung} 
\leavevmode \\Samsung Electronics Co., Ltd:
\newblock Samsung Gear 360,\\
\newblock http://www.samsung.com/global/galaxy/gear-360/ (閲覧日 2019.12.16).
\\

\bibitem[Sattler 2011]{Sattler2011} 
\leavevmode \\T.~Sattler, B.~Leibe and L.~Kobbelt:
\newblock ``Fast Image-Based Localization Using Direct 2D-to-3D Matching'',
\newblock Proceedings of the 2011 IEEE International Conference on Computer Vision, pp.~667--674, 2011.
\\

\bibitem[Scaramuzza 2006]{Scaramuzza2006} 
\leavevmode \\D.~Scaramuzza, A.~Martinelli and R.~Siegwart:
\newblock ``A Toolbox for Easy Calibrating Omnidirectional Cameras'',
\newblock Proceedings of the 2006 IEEE/RSJ International Conference on Intelligent Robots and Systems, pp.~5695--5701, 2006.
\\

%\bibitem[Scaramuzza 2011]{Scaramuzza2011} 
%\leavevmode \\D.~Scaramuzza and F.~Fraundorfer:
%\newblock ``Visual Odometry [Tutorial] Part I: The First 30 Years and Fundamentals'',
%\newblock IEEE Robotics \& Automation Magazine, Vol.~18, No.~4, pp.~80--92, 2011.
%\\

\bibitem[Smith 2013]{Smith2013} 
\leavevmode \\A.~Smith, A.~Doucet, N.~Freitas and N.~Gordon:
\newblock Sequential Monte Carlo Methods in Practice,
\newblock Springer Science \& Business Media, 2013.
\\

%\bibitem[Torii 2007]{Torii2007}
%\leavevmode \\A.~Torii and A.~Imiya:
%\newblock ``The Randomized-Hough-Transform-based Method for Great-Circle Detection on Sphere'',
%\newblock Pattern Recognition Letters, Vol.~28, No.~10, pp.~1186--1192, 2007.
%\\

%\bibitem[Torii 2014]{Torii2014}
%\leavevmode \\A.~Torii, Y.~Dong, M.~Okutomi, J.~Sivic and T.~Pajdra:
%\newblock ``Efficient Localization of Panoramic Images Using Tiled Image Descriptors'',
%\newblock Information and Media Technologies, Vol.~9, No.~3, pp.~351--355, 2014.
%\\

%\bibitem[Triggs 2000]{Triggs2000}
%\leavevmode \\B.~Triggs, P.~F.~McLauchlan, R.~I.~Hartley and A.~W.~Fitzgibbon:
%\newblock ``Bundle Adjustment -- A Modern Synthesis'',
%\newblock Vision Algorithms: Theory and Practice, pp.~298--372, 2000.
%\\

\bibitem[Vakhitov 2016]{Vakhitov2016} 
\leavevmode \\A.~Vakhitov, J.~Funke and F.~Moreno-Noguer:
\newblock ``Accurate and Linear Time Pose Estimation from Points and Lines'',
\newblock Proceedings of the 2016 European Conference on Computer Vision, pp.~583--599, 2016.
\\

%\bibitem[Valgaerts 2012]{Valgaerts2012} 
%\leavevmode \\L.~Valgaerts, A.~Bruhn, M.~Mainberger and J.~Weickert:
%\newblock ``Dense versus Sparse Approaches for Estimating Fundamental Matrix'',
%\newblock International Journal of Computer Vision, Vol.~96, pp.~212--234, 2012.
%\\

%\bibitem[Xu 2009]{Xu2009} 
%\leavevmode \\L.~Xu and E.~Oja:
%\newblock ``Randomized Hough Transform'',
%\newblock Encyclopedia of Artificial Intelligence, pp.~1343--1350, 2009.
%\\

\bibitem[Xu 2017]{Xu2017} 
\leavevmode \\C.~Xu, L.~Zhang, L.~Cheng and R.~Koch:
\newblock ``Pose Estimation from Line Correspondences: A Complete Analysis and A Series of Solutions'',
\newblock IEEE Transactions on Pattern Analysis and Machine Intelligence, Vol.~39, No.~6, pp.~1209--1222, 2017.
\\

%\bibitem[Zhang 2016]{Zhang2016} 
%\leavevmode \\Z.~Zhang, H.~Rebecq, C.~Forster and D.~Scaramuzza:
%\newblock ``Benefit of Large Field-of-View Cameras for Visual Odometry'',
%\newblock Proceedings of 2016 IEEE International Conference on Robotics and Automation, pp.~801--808, 2016.
%\\


%\bibitem[Michael 2012]{Michael2012}
%\leavevmode \\M.~Michael, S.~Shen, K.~Mohna, Y.~Mulgaonkar, V.~Kumar, K.~Nagatani, Y.~Okada, S.~Kiribayashi, K.~Otake, K.~Yoshida, et~al.:
%\newblock ``Collaborative Mapping of an Earthquake-Damaged Building via Ground and Aerial Robots'',
%\newblock Journal of Field Robotics, Vol.~29, No.~5, pp.~832--841, 2012.
%\\
%
%\bibitem[Sonnemann 2006]{Sonnemann2006}
%\leavevmode \\T.~Sonnemann, M.~Sauerbier, F.~Remondino and G.~Schrotter:
%\newblock ``Reality-based 3D Modeling of the Angkorian Temples using Aerial Images'',
%\newblock BAR International Series, Vol.~1568, p.~573, 2006.
%\\
%
%\bibitem[Bruno 2010]{Bruno2010}
%\leavevmode \\F.~Bruno, S.~Bruno, G.~De~Sensi, M.~-L.~Luch, S.~Mancuso and M.~Muzzupappa:
%\newblock ``From 3D Reconstruction to Virtual Reality: A Complete Methodology for Digital Archaeological Exhibition'',
%\newblock Journal of Cultural Heritage, Vol.~11, No.~1, pp.~42--49, 2010.
%\\
%
%\bibitem[Suveg 2004]{Suveg2004}
%\leavevmode \\I.~Suveg and G.~Vosselman:
%\newblock ``Reconstruction of 3D Building Models from Aerial Images and Maps'',
%\newblock ISPRS Journal of Photogrammetry and Remote Sensing, Vol.~58, No.~3, pp.~202--224, 2004.
%\\

\end{mythebibliography}